Eye Fitting Straight Lines in the Modern Era

### 2022-10-06 supplementary-material/you-draw-it-eyefitting-analysis.Rmd
adjusted naming of supplementary-material

# eyefitting_parameter_details <- read_csv("eyefitting-parameter-details.csv")
eyefitting_parameter_details <- read_csv("https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/raw/main/analysis/eyefitting-feedback-data.csv")
eyefitting_parameter_details %>% knitr::kable()

>>>>

# eyefitting_parameter_details <- read_csv("eyefitting-parameter-details.csv")
eyefitting_parameter_details <- read_csv("https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/raw/main/analysis/eyefitting-parameter-details.csv")
eyefitting_parameter_details %>% knitr::kable()
